---
title: "Crime Reports in Seattle"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
source('./scripts/graphthree.R')
source('./scripts/graphone.R')
source('./scripts/graphtwo.R')
source('./scripts/summary_info.R')
```

## Motivation for the Project

Seattle, one of the most popular cities in the US, is known to have a high population.  
Due to its high population, crime is unavoidable in the city. Recognizing the concern, 
we desire to create a data visualization that visually conveys the type and location of reported crimes. 

We are interested in the topic because identifying patterns in past crimes
not only help professionals make informed decisions to combat the war with 
crime but also informs the general public about the critical information regarding 
public safety. Police officers, government officials, and others can use insights 
from this data to try implementing and enforcing different solutions to reduce crime rates. 
We believe that this type of data-driven decision making can have a positive impact 
on cities all around the world.

To obtain credible data,  we collected our data sources are from Seattle.gov. 
The Seattle Police Department created all three data that we used for the project. 
Dataset 1 provides information about criminal incidents from 2008-present day, 
as well as the type of crime, its location, and how frequently that type occurs.

```{r echo = FALSE}
kable(agg_table, caption = "Crime Information by Sector", 
      col.names = c("Sectors", "Number of Crimes", "Number of Calls to Police"))
```

## Call Data of SPD Communications Center
```{r echo = FALSE}
pie_chart
```

This data comes from Seattle Police Department's Communications Center's record of log calls, 
including 911 calls, etc.The pie chart shows the top 10 most common Initial Call Type received 
from 2008 to present day. Of these call types, the most common ones are simple Premise Checks 
and Traffic Violations. However, there are also more serious crimes such as Burglary and Narcotics. 
 

## Crime Report from 2008-present day
```{r echo=FALSE}
graph_one
```
A precinct is an area whose boundaries are determined by the police for their investigative purposes. 
As indicated by this graph, the North precinct of Seattle is the most dangerous based on the number of 
crimes that have occured from 2008 to present day.


## Number of Crime Reports in Seattle Neighborhood
```{r echo=FALSE}
bar_chart
```

This data comesfrom 
The Seattle Police Department provided this data on the Seattle.gov website. 
It includes information about the crime that was reported in different neighborhoods in Seattle. 
There are total 524k rows, and 11 columns and each row is a unique crime reported record. 
The visualization focused on the number of crime reports in different neighborhoods in Seattle

